Somatosensory Response Changes During Illusory Finger Stretching

### 2024-05-14 manuscript.qmd
Removed forced tinytex install
Testing full analysis from raw data

processdata <- 0
# the processdata flag has two levels:
# 0 - just produce the manuscript and all analyses and figures from processed EEG data
# 1 - do all analyses from scratch using the raw EEG data

@@

if (!is_tinytex()){install_tinytex()}

>>>>

processdata <- 1
# the processdata flag has two levels:
# 0 - just produce the manuscript and all analyses and figures from processed EEG data
# 1 - do all analyses from scratch using the raw EEG data

@@

# if (!is_tinytex()){install_tinytex()}
